SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-07 scipy-1.0/paper.tex
MAINT: reviewer comments PR 234
* apply the patch provided by Stefan to
improve articles PR 234

The SciPy test suite is orchestrated by a continuous integration matrix that
includes POSIX and Windows (32/64-bit) platforms managed by Travis CI and
AppVeyor, respectively. Our tests cover Python versions 2.7, 3.4, 3.5, 3.6, and
include code linting with \texttt{pyflakes} and \texttt{pycodestyle}. There
are more than \num{13000}~unit tests in the test suite, which is written for usage
with the \texttt{pytest}\cite{pytest} framework.
Test coverage at the SciPy~1.0 release point (Figure~\ref{fig:coverage}) was at
87\% for Python code according to \texttt{pytest-cov}\cite{pytest-cov}.
Coverage for compiled (C, C++, and Fortran) code is still being implemented.
Documentation for the code is automatically built and published by
the CircleCI service to facilitate evaluation of documentation changes /
integrity.  Our full test suite also passes with PyPy3\cite{Bolz:2009:TMP:1565824.1565827}, a just-in-time compiled
version of the Python language.

>>>>

Test-driven development has been described as a way to manage fear and
uncertainity when making code changes\cite{TDD-Beck}. For each component of SciPy, we write multiple small executable
tests that verify its intended behavior. The collection of these, known as a \emph{test suite}, increases confidence in
the correctness and accuracy of the library, and lets us make code modifications known not to alter desired behavior. Monitoring the number of lines
of code in SciPy covered by unit tests is one way we maintain
some certainty that changes and new features are correctly implemented.
The SciPy test suite is orchestrated by a continuous integration matrix that
includes POSIX and Windows (32/64-bit) platforms managed by Travis CI and
AppVeyor, respectively. Our tests cover Python versions 2.7, 3.4, 3.5, 3.6, and
include code linting with \texttt{pyflakes} and \texttt{pycodestyle}. There
are more than \num{13000}~unit tests in the test suite, which is written for usage
with the \texttt{pytest}\cite{pytest} framework.
Test coverage at the SciPy~1.0 release point (Figure~\ref{fig:coverage}) was at
87\% for Python code according to \texttt{pytest-cov}\cite{pytest-cov} and
45\% for compiled (C, C++, and Fortran) code according to \texttt{gcov}\cite{gcov}.
Documentation for the code is automatically built and published by
the CircleCI service to facilitate evaluation of documentation changes /
integrity.  Our full test suite also passes with PyPy3\cite{Bolz:2009:TMP:1565824.1565827}, a just-in-time compiled
version of the Python language.
